Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-15 draft.tex
add experimental results from other methods

		The model that achieved the best results was trained on the first
		10000 samples of the dataset and evaluated on the rest evaluated using the methods
		previously described. It has an evaluation accuracy of 96.3\% with the default threshold
		of 0.5, with an EER of approximately 0.03214. This outperforms other results tested in the
		original paper on this dataset \cite{muller_does_2022}. This result also exceeds some
		other results tested on this dataset, such as an example \cite{yang_robust_2024} produced
		using a variety of imperceptible features and trained on the ASV2019 dataset, while
		underperforming one other method \cite{ranjan_statnet_2022} that made use of raw
		waveform-based features, training on 70 percent of the data in the dataset, validating on
		10 percent and testing on the remaining 20 percent.

@@

		\subsubsection{Best-Performing Model}

>>>>

		The model that resulted in the best accuracy and EER had the standard feature set and was
		paired with a terminus with three hidden perceptron layers. We trained this model on the
		first 10000 samples of the dataset, and we evaluated it on the rest of the dataset using
		the methods previously described. It demonstrated an evaluation accuracy of 96.3\% with
		the default threshold of 0.5, as well as an EER of approximately 0.03214. The best AUC
		score, however, was achieved in another experiment, where the model had expended pitch
		fluctuations and a terminus model without hidden layers, with a value of 0.92727.
		\subsubsection{Comparison to Other Methods}
			\begin{table}
				\caption{A summary of the experimental results of other methods that have been
				evaluated against the same dataset. (When multiple experiments with one method
				were done, the best result was used for this table. The results only include
				evaluations on the full length samples, and not cropped versions, as we tested on
				the full-length samples)}
				\begin{tabular}{c | c}
					Model Architecture & EER \\
					RawGAT-ST \cite{muller_does_2022} & 0.37154 \\
					RawNet2 \cite{muller_does_2022} & 0.37819 \\
					MesoInception \cite{muller_does_2022} & 0.37414 \\
					LCNN \cite{muller_does_2022} & 0.65559 \\
					LCNN-Attention \cite{muller_does_2022} & 0.66684 \\
					LCNN-LSTM \cite{muller_does_2022} & 0.61500 \\
					LSTM \cite{muller_does_2022} & 0.53711 \\
					MesoNet \cite{muller_does_2022} & 0.46939 \\
					ResNet18 \cite{muller_does_2022} & 0.49759 \\
					Transformer \cite{muller_does_2022} & 0.43775 \\
					CRNNSpoof \cite{muller_does_2022} & 0.44500 \\
					RawPC \cite{muller_does_2022} & 0.45715 \\
					ResNet18 \cite{yang_robust_2024} & 0.2748 \\
					Selection \cite{yang_robust_2024} & 0.2598 \\
					Fusion \cite{yang_robust_2024} & 0.2427 \\
					STATNet \cite{ranjan_statnet_2022} & \textbf{0.00199} \\
					ASSERT \cite{yi_audio_2023} & 0.2473 \\
					LCNN \cite{yi_audio_2023} & 0.3514 \\
					GMM \cite{yi_audio_2023} & 0.3749 \\
				\label{table:other_results}
			In order to contextualize our results, we will compare them to other results produced
			using tests on the same dataset. Table \ref{table:other_results} presents some
			experimental results that other methods have achieved on this dataset, sorted by
			source and model architecture. The results are given in EER, and the best result is in
			bold. In comparison to the other methods, our method performs very well, only beaten
			out by one other \cite{ranjan_statnet_2022}, which uses an expanded RawNet2-based
			network, taking the raw waveform as an input. They trained their method on 70\% of the
			dataset, used 10\% for validation and the remaining 20\% for testing. This indicates a
			potential for raw-waveform based learned feature in the accurate detection of audio
			deepfakes, but does not offer a clear path for explainability, as the model does not
			make any intrinsic distinction of audio characteristics that humans are able to perceive.
			Our model remains, however, competitive, indicating that it can provide a good base
			for trustworthy explanations.

@@

		\subsubsection{Model with Standard Feature Set and Complex Terminus}
